Computing Exact Restricted Isometry Constants via\\ Mixed Integer Semidefinite Programming

### 2016-03-12 RIP-MISDP-Paper/IEEE_RIP-MISDP.tex
restructured abstract

\begin{abstract}
An important task in compressed sensing is finding the sparsest solution to an underdetermined system of linear equations. An outstanding result is that, under certain conditions, this is equivalent to minimizing the 1-Norm and thus
solving a linear program. One such condition is the restricted isometry property for which no efficient algorithms are known to compute the optimal constants, the so called restricted isometry constants. In this paper we propose a
mixed integer semidefinite program for computing these constants. Numerical results are presented comparing this to ealier SDP relaxations for the same task.
\end{abstract}

>>>>

\noindent
\begin{abstract}
  One of the fundamental tasks in compressed sensing is finding the
  sparsest solution to an underdetermined system of linear equations. It is
  well known that although this problem is \NP-hard, under certain
  conditions it can be solved by using a linear program which minimizes the
  1-norm. The restricted isometry property has been one of the key
  conditions in this context. However, computing the best constants for
  this condition is itself \NP-hard. In this paper we propose a
  mixed-integer semidefinite programming approach for computing these
  optimal constants. This also subsumes sparse principal component
  analysis. Computational results with this approach allow to evaluate
  ealier SDP relaxations and show that their quality is limited.
\end{abstract}
